---
title: "NYSEMonitor"
author: "Igor Lapkiewicz and Filip Nowakowski"
date: "16 05 2021"
output:
  html_document:
    collapsed: false
    number_sections: true
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    includes:
       in_header: myheader.html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#Create myheader.html
fileConn <- file("myheader.html")
writeLines('<link rel="stylesheet" href="https://maxcdn.bootstrapcdn.com/bootstrap/4.0.0/css/bootstrap.min.css" integrity="sha384-Gn5384xqQ1aoWXA+058RXPxPg6fy4IWvTNh0E263XmFcJlSAwiGgFAW/dAiS6JXm" crossorigin="anonymous">', fileConn)
close(fileConn)
```

# NYSE Monitor Project
## About authors
Igor Łapkiewicz - second year master's student in Data Science and Business Analytics at University of Warsaw Economics Faculty. Python and R enthusiast interested in data analytics.

Filip Nowakowski - second year master's student in Data Science and Business Analytics at University of Warsaw Economics Faculty. R and Power Platform fan, passionate about visualizing data.

## Project description

NYSE Monitor project aims to automatically generate reports about different sectors of stock market. A simple change in .Rmd file allows user to swap between pre-coded sectors and generate multiple reports that gather data from selected day until recent most available one. Because of this no actual data commentary can be seen in the report as everything is automated. Interpretation must be done by you - the reader.

Report is divided into following parts:

__Sector outlook__
Basic information and key statistics of the whole sector
    
__Top Gainers__
Information and simple forecast of top 5 stocks with highest growth
 
__Top gainers simple trading strategy results__
Results of simple trading strategy implemented for 5 stocks from previous part

__Non-technical approach__
A more expaned look at stock analysis employing techniques not based on typical stock charts

```{r data-acquisition-functions, include=FALSE}
#install.packages("xts", repos="http://cloud.r-project.org") # for working with time series
#install.packages("quantmod",repos = "http://cran.us.r-project.org") # for getting Yahoo finance data automatically

library(xts)
library(quantmod)

get_tickers <- function(x) {
  #first ticker group
  if(x==1){
    Healthcare_tickers <- getSymbols(c("BHP",	"LIN",	"BBL",	"VALE",	"RIO",	
                                       "CTA-PB",	"CTA-PA",	"APD",	"ECL",	"NEM",	
                                       "FCX",	"SCCO",	"DOW",	"DD",	"GOLD",	"PPG",	
                                       "CRH",	"LYB",	"IFF",	"NTR",	"CTVA",	"MT",	
                                       "NUE",	"FNV",	"PKX",	"SHW",	"VMC",	"MLM",	
                                       "WPM",	"CE",	"ALB",	"AEM",	"AVTR",	"SUZ",	"EMN",	
                                       "AVTR-PA",	"FMC",	"ACH",	"JHX",	"VEDL",	"MOS",	
                                       "SBSW",	"STLD",	"TECK",	"WLK",	"SID",	"CX",	"RPM",	
                                       "SMG",	"KL",	"SQM",	"CF",	"AU",	"GGB",	"GFI",	"RS",	
                                       "KGC",	"CLF",	"WFG",	"ICL",	"RGLD",	"AXTA",	"BAK",	
                                       "TX",	"OLN",	"PAAS",	"AA",	"MDU",	"X",	"HUN",	"EXP",
                                       "CC",	"ESI",	"ASH",	"AUY",	"UFPI",	"AVNT",	"MP",	"HL",	
                                       "GRA",	"UNVR",	"BCPC",	"KWR",	"SSRM",	"AG",	"CMC",	"NEU",	
                                       "SUM",	"NGVT",	"SXT",	"AGI",	"ZY",	"TRQ",	"CBT",	"FUL",	
                                       "WDFC",	"TROX",	"AMRS",	"HMY",	"UFS",	"SCL",	"BVN",	"MEOH",	
                                       "MTX",	"LTHM",	"CDE",	"BCC",	"TSE",	"IOSP",	"CSTM",	"CMP",	"OR",	
                                       "CGAU",	"PVG",	"PQG",	"EGO",	"HBM",	"KALU",	"EVA",	"KRO",	
                                       "GCP",	"FOE",	"DNMR",	"SAND",	"LAC",	"MTRN",	"NEXA",	"SCHN",	
                                       "SWM",	"SA",	"LOMA",	"CENX",	"FSM",	"OEC",	"RFP",	"MGPI",	
                                       "KRA",	"EXK",	"DRD",	"GPRE",	"MERC",	"NP",	"WLKP",	"USCR",	
                                       "LGO",	"PLL",	"HCC",	"ASIX",	"GATO",	"USLM",	"KOP",	"VHI",	
                                       "FF",	"TMST",	"CPAC",	"GLT",	"BIOX",	"UAN",	"SXC",	"VRS",	
                                       "AVD",	"TG",	"MSB",	"CLW",	"RYAM",	"IPI",	"ZEUS",	"HWKN",	
                                       "ODC",	"AMR",	"CINR",	"TREC",	"LXU",	"SPPP",	"USAP",	"CGA",	
                                       "GURE",	"IFFT"),
                                     from = "2020-01-01")
    
    Healthcare_tickers_xts <- BHP$BHP.Close
    counter <- length(Healthcare_tickers)
    for (ticker in Healthcare_tickers) {
      Object = get(paste0(ticker))
      Object = Object[, paste0(ticker,'.Close')]
      Healthcare_tickers_xts <- cbind(Healthcare_tickers_xts,Object)
      
    }
    Healthcare_tickers_xts$BHP.Close.1 <- NULL
    names <- colnames(Healthcare_tickers_xts)
    new_names <- 0
    for (i in names){
      name <- unlist(strsplit(i[1], split='.', fixed=TRUE))[1]
      new_names <- c(new_names,name)
    }
    new_names <- new_names[-(1:1)]
    colnames(Healthcare_tickers_xts) <- new_names
    return(Healthcare_tickers_xts)
    #second ticker group
  } else if (x==2) {
    BasicMaterials_tickers <- getSymbols(c("UFS",	"BVN",	"MEOH",	"MTX",	"BCC",	"LTHM",	"TSE",	"CDE",
                                           "IOSP",	"CSTM",	"CMP"),
                                     from = "2020-01-01")
    
    BasicMaterials_tickers_xts <- UFS$UFS.Close
    counter <- length(BasicMaterials_tickers)
    for (ticker in BasicMaterials_tickers) {
      Object = get(paste0(ticker))
      Object = Object[, paste0(ticker,'.Close')]
      BasicMaterials_tickers_xts <- cbind(BasicMaterials_tickers_xts,Object)
      
    }
    BasicMaterials_tickers_xts$UFS.Close.1 <- NULL
    names <- colnames(BasicMaterials_tickers_xts)
    new_names <- 0
    for (i in names){
      name <- unlist(strsplit(i[1], split='.', fixed=TRUE))[1]
      new_names <- c(new_names,name)
    }
    new_names <- new_names[-(1:1)]
    colnames(BasicMaterials_tickers_xts) <- new_names
    return(BasicMaterials_tickers_xts)
  } else if (x==3) {
    
  }
}


```

```{r data-acquistion-choice, include=FALSE}
#choce sector of NYSE Stock Market here by number in get_tickers()
tickers <- get_tickers(1)
```

# Sector outlook
  One look is all it takes. With this simple chart we see every listed company in the chosen sector. Those in green and green-ish colorshad a positive return while those in red and red-ish colors saw a decline in their price.
```{r treemap-libs,include=FALSE}
#install.packages("treemap", repos="http://cloud.r-project.org")
#install.packages("RColorBrewer", repos="http://cloud.r-project.org")
library(treemap)
library(RColorBrewer)
```

```{r treemap-chunk, out.width = '100%', echo=FALSE}
group <- colnames(tickers)
value <- 0
value_for_vSize <- 0
weight <- 0
for (ticker in group ){
  #vector of percentage change for display
  number <- as.numeric(last(tickers[, paste0(ticker)])) / as.numeric(first(tickers[, paste0(ticker)]))
  number <- number * 100
  number <- round(number,digits=2)
  value_for_vSize <- c(value_for_vSize,number)
  number <- number -100
  value <- c(value,number)
  #vector of last value for size weight
  number <- as.numeric(last(tickers[, paste0(ticker)]))
  weight <- c(weight,number)
}
value_for_vSize <- value_for_vSize[-(1:1)]
value <- value[-(1:1)]
weight <- weight[-(1:1)]

data <- data.frame(group,value, weight, value_for_vSize)

data$label <- paste(data$group, data$value, sep =", %")
treemap(data,
        index=c("label"),
        title = "Whole sector outlook",
        vSize="value_for_vSize",
        vColor="value_for_vSize",
        type="value",
        palette = brewer.pal(n=10, "RdYlGn"),
        mapping = c(80, 100, 150)
)
```

  To quickly show dynamics of the sector we calculate a quick index for the whole sector which can be seen below.
```{r plot-libs, include=FALSE}
library(ggplot2)
```

```{r whole-sector-plot, out.width = '100%', echo=FALSE}
whole_sector_plot <- rowMeans(tickers, na.rm = TRUE)
whole_sector_plot <- as.data.frame(whole_sector_plot)
whole_sector_plot$x <- 1:length(whole_sector_plot$whole_sector_plot)
ggplot(whole_sector_plot, aes(x=x,y=whole_sector_plot)) +
  geom_line() +
  theme_light() +
  ggtitle("Whole sector index") +
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.text.x=element_blank())
```

## Sector statistics

  In this sub-part of the report you can find a more detailed breakdown of the sector represented in the table below.
```{r simple-statistics, include=FALSE}
gainers <- sum(value>0, na.rm = TRUE)
losers <- sum(value<0, na.rm = TRUE)
total <- length(value)
gainers_avg <- value[value >0]
gainers_avg <- mean(gainers_avg, na.rm = TRUE)
losers_avg <- value[value <0]
losers_avg <- mean(losers_avg, na.rm = TRUE)
sector_avg <- value
sector_avg <- mean(sector_avg, na.rm = TRUE)

```


| Total gainers  | Total losers  | Total  |
|-|-|-|
| `r gainers`  | `r losers`   | `r total` |
| __Avarege gainers change__  | __Average losers change__  | __Average Sector change__  |
| `r gainers_avg`%  | `r losers_avg`%   | `r sector_avg`% |

# Top gainers

  Most exciting companies in the sector are those whose price saw the biggest growth. Here you can find all information about top 5 gainers.
```{r top-gainers, include=FALSE}

group <- colnames(tickers)
tickers_change <- 0
for (ticker in group ){
  #vector of percentage change for display
  number <- as.numeric(last(tickers[, paste0(ticker)])) / as.numeric(first(tickers[, paste0(ticker)]))
  number <- number * 100
  number <- round(number,digits=2)
  tickers_change <- c(tickers_change,number)

}
tickers_change <- tickers_change[-(1:1)]
tickers_change <- as.data.frame(tickers_change)
tickers_change$ticker_code <- group
colnames(tickers_change) <- c("change", "ticker_code")
tickers_change <- tickers_change[order(-tickers_change$change),]

#First top gainer
getSymbols(tickers_change$ticker_code[1], from="2020-01-01")

assign("top_gainer_1", tickers_change$ticker_code[1])
percet_change_1 <- tickers_change$change[1] -100
#Second top gainer
getSymbols(tickers_change$ticker_code[2], from="2020-01-01")

assign("top_gainer_2", tickers_change$ticker_code[2])
percet_change_2 <- tickers_change$change[2] -100
#Third top gainer
getSymbols(tickers_change$ticker_code[3], from="2020-01-01")

assign("top_gainer_3", tickers_change$ticker_code[3])
percet_change_3 <- tickers_change$change[3] -100
#Fourth top gainer
getSymbols(tickers_change$ticker_code[4], from="2020-01-01")

assign("top_gainer_4", tickers_change$ticker_code[4])
percet_change_4 <- tickers_change$change[4] -100
#Fith top gainer
getSymbols(tickers_change$ticker_code[5], from="2020-01-01")

assign("top_gainer_5", tickers_change$ticker_code[5])
percet_change_5 <- tickers_change$change[5] -100

```


```{r libraries-for-forecast, include=FALSE}
library("dygraphs")
library(forecast)
```


## Top 5 stocks with biggest gains

  In this section we chart basic information about each of the top 5 gainers along with a simple forecast done with Neural Network model.
  
<!-- First top gainer-->
### `r tickers_change$ticker_code[1]`
<p> `r tickers_change$ticker_code[1]` value changed by `r percet_change_1`%</p>
```{r top-gainer-1, out.width = '100%', echo=FALSE}
chartSeries(get(top_gainer_1),
            type="line",
            name=tickers_change$ticker_code[1],
            theme=chartTheme('white'))
```

`r tickers_change$ticker_code[1]` forecast

```{r top-gainer-1-forecast, out.width = '100%', echo=FALSE}
a <- get(top_gainer_1)
nnmodel <-nnetar(a[, paste0(top_gainer_1,".Close")])
nnmodel_forecast <-forecast(nnmodel,h=36,PI=T)

data <- nnmodel_forecast$x
lower <- nnmodel_forecast$lower[,2]
upper <- nnmodel_forecast$upper[,2]
pforecast <- nnmodel_forecast$mean
graph_data <- cbind(data, lower, upper,
                    pforecast)

dygraph(graph_data, main = "Forecast with Neural Network") %>% 
  dyRangeSelector() %>% 
  dySeries(name = "data", label = "Recorded value") %>%
  dySeries(c("lower","pforecast","upper"), label = "Forecast") %>%
  dyLegend(show = "always", hideOnMouseOut = FALSE) %>%
  dyAxis("y", label = "Value in USD") %>%
  dyHighlight(highlightCircleSize = 5,
              highlightSeriesOpts = list(strokeWidth = 2)) %>%
  dyOptions(axisLineColor = "navy", gridLineColor = "grey")
```

<!-- Second top gainer-->
### `r tickers_change$ticker_code[2]`
<p> `r tickers_change$ticker_code[2]` value changed by `r percet_change_2`%</p>
```{r top-gainer-2, out.width = '100%', echo=FALSE}
chartSeries(get(top_gainer_2),
            type="line",
            name=tickers_change$ticker_code[2],
            theme=chartTheme('white'))
```

`r tickers_change$ticker_code[2]` forecast

```{r top-gainer-2-forecast, out.width = '100%', echo=FALSE}
a <- get(top_gainer_2)
nnmodel <-nnetar(a[, paste0(top_gainer_2,".Close")])
nnmodel_forecast <-forecast(nnmodel,h=36,PI=T)

data <- nnmodel_forecast$x
lower <- nnmodel_forecast$lower[,2]
upper <- nnmodel_forecast$upper[,2]
pforecast <- nnmodel_forecast$mean
graph_data <- cbind(data, lower, upper,
                    pforecast)

dygraph(graph_data, main = "Forecast with Neural Network") %>% 
  dyRangeSelector() %>% 
  dySeries(name = "data", label = "Recorded value") %>%
  dySeries(c("lower","pforecast","upper"), label = "Forecast") %>%
  dyLegend(show = "always", hideOnMouseOut = FALSE) %>%
  dyAxis("y", label = "Value in USD") %>%
  dyHighlight(highlightCircleSize = 5,
              highlightSeriesOpts = list(strokeWidth = 2)) %>%
  dyOptions(axisLineColor = "navy", gridLineColor = "grey")
```


<!-- Third top gainer-->
### `r tickers_change$ticker_code[3]`
<p> `r tickers_change$ticker_code[3]` value changed by `r percet_change_3`%</p>
```{r top-gainer-3, out.width = '100%', echo=FALSE}
chartSeries(get(top_gainer_2),
            type="line",
            name=tickers_change$ticker_code[3],
            theme=chartTheme('white'))
```

`r tickers_change$ticker_code[3]` forecast

```{r top-gainer-3-forecast, out.width = '100%', echo=FALSE}
a <- get(top_gainer_3)
nnmodel <-nnetar(a[, paste0(top_gainer_3,".Close")])
nnmodel_forecast <-forecast(nnmodel,h=36,PI=T)

data <- nnmodel_forecast$x
lower <- nnmodel_forecast$lower[,2]
upper <- nnmodel_forecast$upper[,2]
pforecast <- nnmodel_forecast$mean
graph_data <- cbind(data, lower, upper,
                    pforecast)

dygraph(graph_data, main = "Forecast with Neural Network") %>% 
  dyRangeSelector() %>% 
  dySeries(name = "data", label = "Recorded value") %>%
  dySeries(c("lower","pforecast","upper"), label = "Forecast") %>%
  dyLegend(show = "always", hideOnMouseOut = FALSE) %>%
  dyAxis("y", label = "Value in USD") %>%
  dyHighlight(highlightCircleSize = 5,
              highlightSeriesOpts = list(strokeWidth = 2)) %>%
  dyOptions(axisLineColor = "navy", gridLineColor = "grey")
```

<!-- Fourth top gainer-->
### `r tickers_change$ticker_code[4]`
<p> `r tickers_change$ticker_code[4]` value changed by `r percet_change_4`%</p>
```{r top-gainer-4, out.width = '100%', echo=FALSE}
chartSeries(get(top_gainer_4),
            type="line",
            name=tickers_change$ticker_code[4],
            theme=chartTheme('white'))
```

`r tickers_change$ticker_code[4]` forecast

```{r top-gainer-4-forecast, out.width = '100%', echo=FALSE}
a <- get(top_gainer_4)
nnmodel <-nnetar(a[, paste0(top_gainer_4,".Close")])
nnmodel_forecast <-forecast(nnmodel,h=36,PI=T)

data <- nnmodel_forecast$x
lower <- nnmodel_forecast$lower[,2]
upper <- nnmodel_forecast$upper[,2]
pforecast <- nnmodel_forecast$mean
graph_data <- cbind(data, lower, upper,
                    pforecast)

dygraph(graph_data, main = "Forecast with Neural Network") %>% 
  dyRangeSelector() %>% 
  dySeries(name = "data", label = "Recorded value") %>%
  dySeries(c("lower","pforecast","upper"), label = "Forecast") %>%
  dyLegend(show = "always", hideOnMouseOut = FALSE) %>%
  dyAxis("y", label = "Value in USD") %>%
  dyHighlight(highlightCircleSize = 5,
              highlightSeriesOpts = list(strokeWidth = 2)) %>%
  dyOptions(axisLineColor = "navy", gridLineColor = "grey")
```


<!-- Fith top gainer-->
### `r tickers_change$ticker_code[5]`
<p> `r tickers_change$ticker_code[5]` value changed by `r percet_change_5`%</p>
```{r top-gainer-5, out.width = '100%', echo=FALSE}
chartSeries(get(top_gainer_5),
            type="line",
            name=tickers_change$ticker_code[5],
            theme=chartTheme('white'))
```

`r tickers_change$ticker_code[5]` forecast

```{r top-gainer-5-forecast, out.width = '100%', echo=FALSE}
a <- get(top_gainer_5)
nnmodel <-nnetar(a[, paste0(top_gainer_5,".Close")])
nnmodel_forecast <-forecast(nnmodel,h=36,PI=T)

data <- nnmodel_forecast$x
lower <- nnmodel_forecast$lower[,2]
upper <- nnmodel_forecast$upper[,2]
pforecast <- nnmodel_forecast$mean
graph_data <- cbind(data, lower, upper,
                    pforecast)

dygraph(graph_data, main = "Forecast with Neural Network") %>% 
  dyRangeSelector() %>% 
  dySeries(name = "data", label = "Recorded value") %>%
  dySeries(c("lower","pforecast","upper"), label = "Forecast") %>%
  dyLegend(show = "always", hideOnMouseOut = FALSE) %>%
  dyAxis("y", label = "Value in USD") %>%
  dyHighlight(highlightCircleSize = 5,
              highlightSeriesOpts = list(strokeWidth = 2)) %>%
  dyOptions(axisLineColor = "navy", gridLineColor = "grey")
```


## Top gainers statistical analysis

  In this section we can find a more detailed anlysis of 5 charts we saw in the previous section.Each ticker plot is given a Moving Average Convergence Divergence part, Volume graph, Commodity Channel Index and three ROCs for 200, 50 and 22 periods (in blue, red and green respectively)
  
### `r tickers_change$ticker_code[1]` analysis
```{r top-gainer-statistical-a, out.width = '100%', echo=FALSE}

chartSeries(get(top_gainer_1), theme="white",
            name=tickers_change$ticker_code[1],
            type = c("auto", "matchsticks"), 
            show.grid = TRUE,
            major.ticks='auto', minor.ticks=TRUE,
            multi.col = FALSE,
            TA=c(addMACD(),addVo(),addCCI(),addSMA(n=200,col = 'blue'),addSMA(n=50,col = 'red'),addSMA(n=22,col = 'green'),
                 addROC(n=200,col = 'blue'),addROC(n=50,col = 'red'),addROC(n=22,col = 'green'))) # rate of change
```

### `r tickers_change$ticker_code[2]` analysis
```{r top-gainer-statistical-b, out.width = '100%', echo=FALSE}

chartSeries(get(top_gainer_2), theme="white",
            name=tickers_change$ticker_code[2],
            type = c("auto", "matchsticks"), 
            show.grid = TRUE,
            major.ticks='auto', minor.ticks=TRUE,
            multi.col = FALSE,
            TA=c(addMACD(),addVo(),addCCI(),addSMA(n=200,col = 'blue'),addSMA(n=50,col = 'red'),addSMA(n=22,col = 'green'),
                 addROC(n=200,col = 'blue'),addROC(n=50,col = 'red'),addROC(n=22,col = 'green'))) # rate of change
```

### `r tickers_change$ticker_code[3]` analysis
```{r top-gainer-statistical-c, out.width = '100%', echo=FALSE}

chartSeries(get(top_gainer_3), theme="white",
            name=tickers_change$ticker_code[3],
            type = c("auto", "matchsticks"), 
            show.grid = TRUE,
            major.ticks='auto', minor.ticks=TRUE,
            multi.col = FALSE,
            TA=c(addMACD(),addVo(),addCCI(),addSMA(n=200,col = 'blue'),addSMA(n=50,col = 'red'),addSMA(n=22,col = 'green'),
                 addROC(n=200,col = 'blue'),addROC(n=50,col = 'red'),addROC(n=22,col = 'green'))) # rate of change
```

### `r tickers_change$ticker_code[4]` analysis
```{r top-gainer-statistical-d, out.width = '100%', echo=FALSE}

chartSeries(get(top_gainer_4), theme="white",
            name=tickers_change$ticker_code[4],
            type = c("auto", "matchsticks"), 
            show.grid = TRUE,
            major.ticks='auto', minor.ticks=TRUE,
            multi.col = FALSE,
            TA=c(addMACD(),addVo(),addCCI(),addSMA(n=200,col = 'blue'),addSMA(n=50,col = 'red'),addSMA(n=22,col = 'green'),
                 addROC(n=200,col = 'blue'),addROC(n=50,col = 'red'),addROC(n=22,col = 'green'))) # rate of change
```

### `r tickers_change$ticker_code[5]` analysis
```{r top-gainer-statistical-e, out.width = '100%', echo=FALSE}

chartSeries(get(top_gainer_5), theme="white",
            name=tickers_change$ticker_code[5],
            type = c("auto", "matchsticks"), 
            show.grid = TRUE,
            major.ticks='auto', minor.ticks=TRUE,
            multi.col = FALSE,
            TA=c(addMACD(),addVo(),addCCI(),addSMA(n=200,col = 'blue'),addSMA(n=50,col = 'red'),addSMA(n=22,col = 'green'),
                 addROC(n=200,col = 'blue'),addROC(n=50,col = 'red'),addROC(n=22,col = 'green'))) # rate of change
```

# Top gainers simple trading strategy results

  One of the most common question we always ask ourselves is how well we would have done by investing in a certain stock. In this part we showcase a simple trading strategy for each of the top 5 gainers. Strategy is based on Variable SMA.
```{r investment-strategies-libs, include=FALSE}
library(PerformanceAnalytics) # performance and risk management
library(TTR)
library(knitr)
```

### Investment in `r tickers_change$ticker_code[1]`

```{r inv-strategy-1, out.width = '100%', echo=FALSE}
data <- get(top_gainer_1)
data <- data[,4]
sma <- SMA(Cl(data), n=50)
macd <- MACD(data, nFast=12, nSlow=26, nSig=50, maType=SMA, percent = FALSE)
signal <- Lag(ifelse(macd$macd < macd$signal, -1, 1))
returns <- ROC(data)*signal
returns <- na.omit(returns)
portfolio <- exp(cumsum(returns))
charts.PerformanceSummary(returns, main = "Performance Summary Chart")
```

### Investment in `r tickers_change$ticker_code[2]`

```{r inv-strategy-2, out.width = '100%', echo=FALSE}
data <- get(top_gainer_2)
data <- data[,4]
sma <- SMA(Cl(data), n=50)
macd <- MACD(data, nFast=12, nSlow=26, nSig=50, maType=SMA, percent = FALSE)
signal <- Lag(ifelse(macd$macd < macd$signal, -1, 1))
returns <- ROC(data)*signal
returns <- na.omit(returns)
portfolio <- exp(cumsum(returns))
charts.PerformanceSummary(returns, main = "Performance Summary Chart")
```

### Investment in `r tickers_change$ticker_code[3]`

```{r inv-strategy-3, out.width = '100%', echo=FALSE}
data <- get(top_gainer_3)
data <- data[,4]
sma <- SMA(Cl(data), n=50)
macd <- MACD(data, nFast=12, nSlow=26, nSig=50, maType=SMA, percent = FALSE)
signal <- Lag(ifelse(macd$macd < macd$signal, -1, 1))
returns <- ROC(data)*signal
returns <- na.omit(returns)
portfolio <- exp(cumsum(returns))
charts.PerformanceSummary(returns, main = "Performance Summary Chart")
```

### Investment in `r tickers_change$ticker_code[4]`

```{r inv-strategy-4, out.width = '100%', echo=FALSE}
data <- get(top_gainer_1)
data <- data[,4]
sma <- SMA(Cl(data), n=50)
macd <- MACD(data, nFast=12, nSlow=26, nSig=50, maType=SMA, percent = FALSE)
signal <- Lag(ifelse(macd$macd < macd$signal, -1, 1))
returns <- ROC(data)*signal
returns <- na.omit(returns)
portfolio <- exp(cumsum(returns))
charts.PerformanceSummary(returns, main = "Performance Summary Chart")
```

### Investment in `r tickers_change$ticker_code[5]`

```{r inv-strategy-5, out.width = '100%', echo=FALSE}
data <- get(top_gainer_1)
data <- data[,4]
sma <- SMA(Cl(data), n=50)
macd <- MACD(data, nFast=12, nSlow=26, nSig=50, maType=SMA, percent = FALSE)
signal <- Lag(ifelse(macd$macd < macd$signal, -1, 1))
returns <- ROC(data)*signal
returns <- na.omit(returns)
portfolio <- exp(cumsum(returns))
charts.PerformanceSummary(returns, main = "Performance Summary Chart")
```

# Non-technical approach

  A technical analysis is certainly a powerful tool but in this section we will present another approach. Because of certain limitations we face with report generating this section will only analyze a single ticker that shows biggest growth.

```{r non-technical-libs, include=FALSE}
library(dplyr)
library(httr)
library(jsonlite)
library(devtools)
library(gtrendsR)
library(tidytext)
library(wordcloud)
library(lubridate)
library(plotly)
library(tidyr)
library(rvest)
library(stringr)
library(DT)

```

  Here is a quick reminder of how the graph of the company with the biggest growth looks like.
```{r top-gainer-1-plot-reminder, out.width = '100%', echo=FALSE}
symbol <- top_gainer_1
chartSeries(get(top_gainer_1),
            type="line",
            name=tickers_change$ticker_code[1],
            theme=chartTheme('white'))

```
  
  ## Google Trends
  
  And now we will gather Google Trend data on that company. Rising intrest in a company can mean many things but it certainly does mean something interesting is going on and usually interesting things mean that there is an opportunity for a good investment.
  
```{r google-trends, out.width = '100%', echo=FALSE, message = FALSE, warning = FALSE}
trends <- gtrends(keyword = symbol, geo = "US", onlyInterest = TRUE)
trends <- trends$interest_over_time %>%
  as_data_frame() %>%
  select(c(date, hits, keyword))
trends$date <- as_tibble(ceiling_date(trends$date, unit = "weeks", change_on_boundary = NULL,
                            week_start = getOption("lubridate.week.start", 1)))
trends %>%  
  plot_ly(x=~date, y=~hits, mode = 'lines', name = "Google Search Trends") %>%
  layout(title = paste0("Interest over Time: ",symbol), yaxis = list(title = "hits"))
```

## News articles

  However, Google Trends alone are not enough, they could be a good source of quick information. For example quick scan of all listed companies names to see which are getting more popular.To get more detailed information we employ article search from the last 30 days using an API.
```{r articles, out.width = '100%', echo=FALSE, message = FALSE, warning = FALSE}
library(config)
url_overview = paste0("https://www.marketwatch.com/investing/stock/",symbol,"/profile")
var_overview = read_html(url_overview)
company <-  var_overview %>% 
  html_nodes('#instrumentname') %>%
  html_text() %>%
  as.character()


#news API Query
url_news = paste0("https://newsapi.org/v2/everything?q=",
                  str_replace_all(top_gainer_1,pattern = " ", replacement = "%20"),
                  "&from=",today()-ddays(29), #last 30 days
                  "&sortBy=relevance&pageSize=100&language=en&apiKey=ProvideAPIKeyHere")

#API json to datatable
results <- GET(url = url_news)
news <- content(results, "text")
news %<>%
  fromJSON(flatten = TRUE) %>% #flatten
  as.data.frame() %>% #make dataframe
  select(c(articles.title, articles.description, articles.content, articles.publishedAt))
datatable(news)
```

## Quick sentiment analysis - word cloud

  Reading all those articles can be very time consuming but thanks to sentiment analysis we can quickly create o word cloud. Obviously this part alone could be extended into tens if not hundreds of reports on one single company with use of cutting edge technology. However, only this small taste of what sentiment analysis offers is presented in this report.
```{r word-cloud, out.width = '100%', echo=FALSE, message = FALSE, warning = FALSE}
news_words <- news %>%
  select(c("articles.title","articles.description", "articles.content", "articles.publishedAt")) %>%
  unnest_tokens(word, articles.description) %>%
  filter(!word %in% append(stop_words$word, values = "chars"), str_detect(word, "^[a-z']+$"))
news_words$date = as_date(news_words$articles.publishedAt)

words_only <- news_words %>%
  count(word, sort =TRUE)

set.seed(1)
wordcloud(words = words_only$word, freq = words_only$n, scale=c(2,.2), max.words=50, colors=brewer.pal(8, "Dark2"))
```








